\section*{Acknowledgements}
I would firstly like to thank my co-supervisors Prof. Franca Fraternali and Dr. Dimitrios Anastasiou for their supervision and in guiding the focus of the research. The work presented herein is the culmination of thousands of hours of dedicated work between the three of us. I thank them for their creativity in the pursuit of scientific thought. 
%
%
\\\\
%
%
I gratefully acknowledge the teaching and assistance of Dr. Laura Masino and Dr. Stephen Martin in experimental biophysical techniques and Dr. Jens Kleinjung in computational methods. I am also indebted to the members of my Thesis Committee: Dr. Paul Driscoll, Dr. Chris Lorenz and Dr. Markus Ralser. I thank them for volunteering their time and their thoughtful feedback throughout the progression of my project.
%
%
\\\\
%
%
Native mass spectrometry and ion mobility measurements were performed together with Ms. Alina Theisen in the laboratory of Prof. Perdita Barran at the Manchester Institute of Biotechnology. 
%
%
\\\\
%
%
It was a fantastic pleasure to work along side Dr. Louise Fets, Dr. Patricia Figueiredo-Nunes, Dr. Fiona Grimm, Ms. Aakriti Jain and Ms. Natalie Bevan in the Anastasiou group; and Dr. Christian Margreitter, Ms. Anna Laddach, Ms. Irene Marzuoli, Mr. Josef Ng and Mr. Marius Kausas in the Fraternali group. I thank them all for their technical and conceptual suggestions, and for their friendship. I especially thank Dr. Louise Fets, with whom measurements of the cellular concentrations of PKM2 ligands were performed.
%
%
\\\\
%
%
Finally, I thank my parents Prof. Andrew Macpherson and Dr. Anja Macpherson, and my brothers Mr. Atholl Macpherson and Mr. Alexander Macpherson, and Ms. Julia Kete for proofreading my manuscript and for their support.
%
%
\\\\
%
%
This work was funded by a MPhil/PhD studentship between King's \textcolor{red}{College} London and the Francis Crick Institute, which receives its core funding from Cancer Research UK, the UK Medical Research Council and the Wellcome Trust.
